---
title: "EDA Assignment"
author: "YIFAN ZHAO"
date: "February 18, 2019"
output: html_document
---
Link to github project: https://github.com/Yzhao7/DataAnalytics-YZ/tree/master/project
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```
1. Setup the question
Refine the problem, the following questions reflect the process of refining the question:
1) How does variable 'price' related to the parameters of bike vendors?
2) The variable 'price' has a negative relationship with the parameters of each bike vendor
3) Does vairable 'price' has a negative relationship with the parameters of each bike vendor? 
*4) Does variable 'price' has a negative relationship with the parameter of vendor 'Ann.Arbor.Speed' (my final question)

2. Describe the data
The data has 1 row of headers, 97 obeserving rows, and 35 variables. 
The following is a description of the variables:

'model' - bike model
'category1' - category of bike models
'category2' - sub-category of bike models under category1
'frame' - the texture of the bike frame
'price' - the price of each model, in $
the bike vendor names (such as 'Albuquerque Cycles', 'Ann Arbor Speed', 'Austin Cruisers'..) - the parameter of each vendor by bike models (I am not quite sure what these variables represent, so I will just call them parameters of each model by vendor), it looks like these parameters has some kind of correlation or relationship with the model or more specifically, model price.

At this point, I want to change the question to 'Does variable 'price' has a negative relationship with the parameter of vendor 'Ann.Arbor.Speed'?'

3. Explore the data
```{r}
bike_vendor <- read.csv("C:/HU/Late Fall 2018/ANLY506/EDA Assignment/bikeVendors.csv")
##
summary(bike_vendor)
## 
str(bike_vendor)
## take a look at the beginning of the dataset to have a good idea of what the dataset look like
head(bike_vendor)
## take a look at the end of the dataset to see if eveything is okay because some dataset has rows that are omitted at the end
tail(bike_vendor)

## Plot variable price on histogram
hist(bike_vendor$price)

## Get the column names
names(bike_vendor)

## check for missing values
is.na(bike_vendor)
```

4. Visualization
```{r}
library(ggplot2)
p <- ggplot(bike_vendor, aes(bike_vendor$price, bike_vendor$Ann.Arbor.Speed))
p + geom_point(colour="dark green", size = 3)+
  geom_smooth(method = "lm", se = FALSE)

## we can see price and Ann.Arbor.Speed parameter has a negative relationship 

relationship <-lm(price ~ Ann.Arbor.Speed, data = bike_vendor)
relationship
plot(relationship)
abline(relationship, col = "green")
```
From the plots above, we can see that in the 1st plot, we can see a parabola-like pattern, which is not good enough.

On normal Q-Q Plot, we can see at the end of the line, the plot deviates from the straight dashed line. This means the residual is not entirely normally distributed.

On the Scale-location plot, it is good to see the line is almost horizontal and the points are spread equally on both side of the line.

5. Report findings, provide answer to the question asked in the first step of EDA

To answer the question, the variable 'price' has a negative relationship with the parameter of vendor 'Ann.Arbor.Speed' and the assumptions are tested.